Low field depolarization of dense NV centers ensemble: application to magnetometry

### 2022-11-04 Talks/Talk Basel 2022/presentation.tex

\begin{document}
\begin{frame}
\maketitle
\begin{center}
\includegraphics[width=\textwidth,height=0.3\textheight,keepaspectratio]{logos}
\end{center}
\end{frame}
%\begin{frame}{Outline}
%\tableofcontents
%\end{frame}
%\section{Physics of the NV center}
\begin{frame}{Preamble : the NV center}
\centering
\includegraphics[width=\textwidth,height=0.9\textheight,keepaspectratio]{Slide  NV properties}
\end{frame}

@@

\begin{frame}{Subject of this presentation}
\centering
\includegraphics[width=\textwidth,height=0.9\textheight,keepaspectratio]{slide_presentation_sujet}
\end{frame}

>>>>

\begin{document}
\begin{frame}
\maketitle
\begin{center}
\includegraphics[width=\textwidth,height=0.3\textheight,keepaspectratio]{logos}
\end{center}
\end{frame}
%\begin{frame}{Outline}
%\tableofcontents
%\end{frame}
%\section{Physics of the NV center}
%\begin{frame}{Preamble : the NV center}
%\centering
%\includegraphics[width=\textwidth,height=0.9\textheight,keepaspectratio]{Slide  NV properties}
%\end{frame}

@@

\begin{frame}{Context: Levitation of micro-diamonds in ion traps}
\centering
\includegraphics[width=0.9\textwidth,height=0.9\textheight,keepaspectratio]{Shema_meca}
\end{frame}

\begin{frame}{Context: Levitation of micro-diamonds in ion traps}
\centering
\includegraphics[width=0.9\textwidth,height=0.9\textheight,keepaspectratio]{Shema_meca_barre}
\end{frame}

\begin{frame}{Depolarization of dense NV ensemble at low magnetic field}
\centering
\includegraphics[width=\textwidth,height=0.9\textheight,keepaspectratio]{slide_presentation_sujet}
\end{frame}
